A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-10-16 alpibot.tex
Correcciones del revisor puntos 1, 2, 3 y 5

%Pulmonary Rehabilitation procedures consist of controlled waking activities and physical exercises that patients perform under the supervision of a physical therapist.

@@

%\IEEEPARstart{C}{hronic} Obstructive Pulmonary Disease (COPD) is an umbrella term that describes several pulmonary affections.  They are characterized as a slowly progressive condition marked by airflow limitation, being cigarette smoking the main etiologic factor~\cite{MacNee2005}. This pathology presents a musculoskeletal atrophy~\cite{Kocsis2016,Wu2012}. In order to carve these after effects a Pulmonary Rehabilitation procedure is a viable treatment for patients.  During this rehabilitation, patients undergo controlled walking activities and physical exercises under the supervision of a physical therapist.   Patients present a severe low oxygen saturation illness and they require effective oxygen supply, particularly when performing physical activities~\cite{Celli2014}.  Hence, patients require to carry with them an oxygen tank for the oxygenotherapy assistance.  However, their own condition prevent them with the ability to precisely carry the often bulky external tank.  This situation entails to find a pragmatic solution to avoid an additional physical therapist to carry the oxygen tank.  This scenario may be aggravated by the fact that this procedure is performed on a rehabilitation gym that could be potentially crowded with several patients, physiologists and physical therapists.

\IEEEPARstart{C}{hronic} Obstructive Pulmonary Disease (COPD) is an umbrella term that describes several pulmonary affections.  They are characterized as a slowly progressive condition marked by airflow limitation, being cigarette smoking the main etiologic factor~\cite{MacNee2005}. This pathology presents a musculoskeletal atrophy~\cite{Kocsis2016,Wu2012}. In order to carve these after effects a Pulmonary Rehabilitation procedure is a viable treatment for patients.  Pulmonary Rehabilitation procedures consist of controlled waking activities and physical exercises that patients perform under the supervision of a physical therapist.  However, COPD patients present a severe low oxygen saturation illness and they require oxygen supply, particularly when performing physical activities~\cite{Celli2014}.  Hence, they are required to carry an oxygen tank for the oxygenotherapy assistance, but their own condition prevent them with the ability to precisely carry the often bulky external tank.  This situation entails to find a pragmatic solution to avoid an additional physical therapist to carry the oxygen tank.  The scenario may be aggravated by the fact that this procedure is performed on a rehabilitation gym that could be potentially crowded with several patients, physiologists and physical therapists.

@@

\noindent where  $c_v$ and $c_{\alpha}$ are constant coefficients used for calibration whose units are expressed in $[\frac{1}{s}]$, and $l_D$ is a constant offset in $[m]$ that is used to customize the desired length of the thread where the robot does not move.   As shown on Figure~\ref{fig:follow_params},  $l_L$ and $l_R$ are thread longitudes in $[m]$  obtained from encoder information from Equation~\ref{eq:encoder_len}, $V_t$ is the estimated forward velocity for the target and finally $\omega_{L}$ are $\omega_{R}$ are the velocity values that are directly used to drive each wheel motor.

@@

The procedure is detailed in Algorithm~\ref{alg:rotateandgoalg}.  The variable $V_r$ is the speed at which the vehicle will rotate on its axis, and $V_f$ is the speed at which the vehicle will move forward once it can move on the subject's direction.  The algorithm requires three parameters, $c_v$ and $c_r$ that regulates the coefficients for the forward and rotation movement, and an additional parameter $Dt_{off}$ that regulates the sensibility of the rotation movement.  The constant parameter $Dm_{off}$ is similar to $l_D$, and is used to customize the length of the thread where the robot does not move at all.

@@

@@

Each control strategy has its advantages, but according various metrics described in this work, the \textit{Follow the thread} strategy had a more desirable behavior, as it tended to follow the leader from a closer distance at all times, while moving in a smooth and predictable way.

@@

\subsection{Validation carrying the oxygen tank}

In order to advance towards the next step, we performed an additional simulated experiment to validate whether or not the selected algorithm could be extended to  handle the oxygen tank.  ALPI works with 5 kg oxygen tanks, which are manufactured locally.

>>>>

%Pulmonary Rehabilitation procedures consist of controlled walking activities and physical exercises that patients perform under the supervision of a physical therapist.

@@

\IEEEPARstart{C}{hronic} Obstructive Pulmonary Disease (COPD) is an umbrella term that describes several pulmonary affections.  They are characterized as a slowly progressive condition marked by airflow limitation, being cigarette smoking the main etiologic factor~\cite{MacNee2005}. This pathology presents a musculoskeletal atrophy~\cite{Kocsis2016,Wu2012}. In order to carve these after effects a Pulmonary Rehabilitation procedure is a viable treatment for patients.  Pulmonary Rehabilitation procedures consist of controlled walking activities and physical exercises that patients perform under the supervision of a physical therapist.  However, COPD patients present a severe low oxygen saturation illness and they require oxygen supply, particularly when performing physical activities~\cite{Celli2014}.  Hence, they are required to carry an oxygen tank for the oxygenotherapy assistance, but their own condition hinders their ability to precisely carry the often bulky external tank.  This situation entails to find a pragmatic solution to avoid an additional physical therapist to carry the oxygen tank.  The scenario may be aggravated by the fact that this procedure is performed on a rehabilitation gym that could be potentially crowded with several patients, physiologists and physical therapists.

@@

\noindent where  $c_v$ and $c_{\alpha}$ are constant coefficients used for calibration whose units are expressed in $[\frac{1}{s}]$, and $l_D$ is a constant offset in $[m]$ that is used to customize the desired length of the thread where the robot does not move.   As shown on Figure~\ref{fig:follow_params},  $l_L$ and $l_R$ are changes in thread longitudes (the length of thread that was released from each reel) in $[m]$  obtained from encoder information from Equation~\ref{eq:encoder_len}, $V_t$ is the estimated forward velocity for the target and finally $\omega_{L}$ are $\omega_{R}$ are the velocity values that are directly used to drive each wheel motor.

@@

The procedure is detailed in Algorithm~\ref{alg:rotateandgoalg}.  The variable $V_r$ is the speed at which the vehicle will rotate on its axis, and $V_f$ is the speed at which the vehicle will move forward once it can move on the subject's direction.  The algorithm requires three parameters, $c_v$ and $c_r$ that regulates the coefficients for the forward and rotation movement, and an additional parameter $Dt_{off}$ that regulates the sensibility of the rotation movement.  The constant parameter $Dm_{off}$ is similar to $l_D$, and is used to customize the length of the thread where the robot does not move at all. Lastly, $base_{vr}$, is another constant used to determine the minimum rotational velocity of the vehicle.

@@

\subsection{Validation carrying the oxygen tank weight}

We performed an additional simulated experiment to validate whether or not the selected algorithm could be extended to handle weight of the real oxygen tank. A common type of tank used in this type of therapies is a 5kg oxygen tank.

@@

Each control strategy has its advantages, but according to various metrics described in this work, the \textit{Follow the thread} strategy had a more desirable behavior, as it tended to follow the leader from a closer distance at all times, while moving in a smooth and predictable way.

@@

% \subsection{Validation carrying the oxygen tank}

% In order to advance towards the next step, we performed an additional simulated experiment to validate whether or not the selected algorithm could be extended to  handle the oxygen tank.  ALPI works with 5 kg oxygen tanks, which are manufactured locally.

% We added on the Webots simulation a 5 kg mass on top of our model, and adjusted the coefficients $c_v$ and $c_{\alpha}$ for the  \textit{Follow the thread}  control strategy.  Results are consistent with the outcomes shown previously on Figures~\ref{fig:simulationresults} and~\ref{fig:realworldresults}.  In Figure~\ref{fig:validationwithtank} it can be seen that the shape of the trajectory follows the patient smoothly, the speed profile also follows stringently the leader speed, and finally the distance between the patient and the robot is maintained within the safe boundaries.  The obtained metrics are 0.2223 for m.t.d. and 1.1068 for t.t.d. which shows that the following behavior is achieved and verifies, from the simulation perspective, the initial feasibility of the control strategy considering the addition of the oxygen tank.
